---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# grouping

<!-- badges: start -->
<!-- badges: end -->

The goal of grouping is to group your data set by a variable and then summarize the remaining numerical variables based on a defined summary function. See the function documentation details for further details.

## Installation

The package 'grouping' is not yet on CRAN, but you can download it from this repository using the following R command:

``` r
devtools::install_github("ashlarnder/grouping", ref="0.1.0")
```


## Example

This is a basic example which shows you the basic use of the function:

```{r example1}
library(grouping)
group_summary(palmerpenguins::penguins, island, mean)
```

This package is a huge time-saver. When working with large, unruly datasets and when working across multiple different datasets, summarizing is a key things you will be doing. This package puts summarizing data at the tip of your finger. This will allow you to apply a cleaner and quicker data analysis. You can even apply two summary functions to the same dataset. 

```{r example 2}
group_summary(mtcars, cyl, c(mean,sd))
```


There is also a check step inherently included in this function. Sometimes you forget which dataset you are using, or sometimes your data is input as the wrong data class. This function will let you know if there is no numerical data to be applied to, by throwing an informative error saying "This does not contain numerical data". I can't actually demonstrate this as the error will prevent the file from knitting.

This is pretty basic, so you should be able to apply it no problem!
